### 2023-10-11 records/manuscript_2023.tex
Polish Code and Figure 2S3

The dynamics of the variance neuron obeys a non-linear differential equation with leak term,
%
\begin{align}
\tau_V \cdot \frac{dr_\mathrm{V}}{dt} = -r_\mathrm{V} + (w_\mathrm{V\leftarrow pE} \cdot r_\mathrm{pE} + w_\mathrm{V\leftarrow nE} \cdot r_\mathrm{nE})^2.
\end{align}
%
The weight $w_\mathrm{V\leftarrow pE}$ represents the connection strength between the pPE neuron and the variance neuron, while  $w_\mathrm{V\leftarrow nE}$ denotes the connection strength between the nPE neuron and the variance neuron. To ensure that the V neuron encodes the variance, we chose a quadratic activation function. In Fig. \ref{fig:Fig_3_S2}, we used a linear activation function to investigate the impact of the input-output transfer function on the weighting of sensory inputs and predictions. The time constant $\tau_V = 5$ s.

@@

\subsubsection{Connections between the PE circuit and the M neuron}
%
While the nPE neurons inhibit the M neuron, the pPE neurons excite it. To ensure that the activities of the memory neurons represent the mean of the sensory stimuli in the lower PE circuit and the mean of the prediction in the higher subnetwork, respectively, the net effect of nPE and pPE neurons must cancel in the steady state (see Analysis in \ref{sec:gain_impact}). Hence, the weights need to account for the neurons' potentially different gain factors ($g_\mathrm{nPE}$ and $g_\mathrm{pPE}$) and the neuron numbers ($N_\mathrm{nPE}$ and $N_\mathrm{pPE}$):
%
\begin{align*}
w_\mathrm{M\leftarrow nE}\  &=\ \frac{-\lambda}{g_\mathrm{nPE} \cdot N_\mathrm{nPE}} \nonumber\\
w_\mathrm{M\leftarrow pE}\  &=\ \frac{\lambda}{g_\mathrm{pPE} \cdot N_\mathrm{pPE}}
\end{align*}
%
where $\lambda$ denotes the speed at which the perfect integrator evolves (lower PE circuit: $\lambda=3\cdot 10^{-3}$  in Fig. \ref{fig:Fig_2} and $\lambda=4.5\cdot 10^{-2}$ otherwise, higher PE circuit:  $\lambda = 7\cdot 10^{-4}$).

@@

\textbf{Figure 2 Supplementary Fig. 2:} Number of time steps were $10^5$ (C-E) or $2\cdot 10^5$ (B) with $400$ (C-E) or $200$ (B) constant values drawn from a uniform distribution with mean of $5$ and variance of $4$. Time step was $0.1$. The connections from the PE neurons to the M or V neuron were altered by a factor $\gamma$ drawn from a normal distribution. If not stated otherwise (in the Figure), the mean of this normal distribution was $1$ and the variance $0$, while the connection probability was $1$. Number of repetitions with different seeds: 10.\\

@@

\textbf{Figure 2 Supplementary Fig. 3:} Number of identical mean-field networks: $1000$.  Simulation time steps = $10^5$.\\

>>>>

The dynamics of the variance neuron obeys a non-linear differential equation with leak term,
%
\begin{align}
\tau_V \cdot \frac{dr_\mathrm{V}}{dt} = -r_\mathrm{V} + (w_\mathrm{V\leftarrow pE} \cdot r_\mathrm{pE} + w_\mathrm{V\leftarrow nE} \cdot r_\mathrm{nE})^2.
\end{align}
%
The weight $w_\mathrm{V\leftarrow pE}$ represents the connection strength between the pPE neuron and the variance neuron, while  $w_\mathrm{V\leftarrow nE}$ denotes the connection strength between the nPE neuron and the variance neuron. To ensure that the V neuron encodes the variance, we chose a quadratic activation function. In Fig. \ref{fig:Fig_3_S2}, we used a linear activation function to investigate the impact of the input-output transfer function on the weighting of sensory inputs and predictions. The time constant $\tau_V$ was 5 s in the mean-field model, and 2 s in the population model (Fig. \ref{fig:Fig_2_S2})., XXX and 0.5 s in 2S3 --> put everything for the not mean field model in the figure captions I would recommend, you can here say that it is only for the mean-field model ... XXX

@@

\subsubsection{Connections between the PE circuit and the M neuron}
%
While the nPE neurons inhibit the M neuron, the pPE neurons excite it. To ensure that the activities of the memory neurons represent the mean of the sensory stimuli in the lower PE circuit and the mean of the prediction in the higher subnetwork, respectively, the net effect of nPE and pPE neurons must cancel in the steady state (see Analysis in \ref{sec:gain_impact}). Hence, the weights need to account for the neurons' potentially different gain factors ($g_\mathrm{nPE}$ and $g_\mathrm{pPE}$) and the neuron numbers ($N_\mathrm{nPE}$ and $N_\mathrm{pPE}$):
%
\begin{align*}
w_\mathrm{M\leftarrow nE}\  &=\ \frac{-\lambda}{g_\mathrm{nPE} \cdot N_\mathrm{nPE}} \nonumber\\
w_\mathrm{M\leftarrow pE}\  &=\ \frac{\lambda}{g_\mathrm{pPE} \cdot N_\mathrm{pPE}}
\end{align*}
%
where $\lambda$ denotes the speed at which the perfect integrator evolves (lower PE circuit: $\lambda=3\cdot 10^{-3}$ for the mean-field model in Fig. \ref{fig:Fig_2},  $\lambda=5\cdot 10^{-2}$ for the population model in Fig. \ref{fig:Fig_2_S2}, and $\lambda=4.5\cdot 10^{-2}$ otherwise; higher PE circuit:  $\lambda = 7\cdot 10^{-4}$). XXX in Fig. \ref{fig:Fig_2_S3} wPE2PE * 100 => I think it is best to put this is the captions, I mean for 2S2 and 2S3 ... for mean field network can be shown here and said "if not stated otherwise in the figures/captions"

@@

\textbf{Figure 2 Supplementary Fig. 2:} Number of time steps were $10^5$ with $200$ constant values drawn from a uniform distribution with mean of $5$ and variance of $4$. Time step was $0.1$. The connections from the PE neurons to the M or V neuron were altered by a factor $\gamma$ drawn from a normal distribution. If not stated otherwise (in the Figure), the mean of this normal distribution was $1$ and the variance $0$, while the connection probability was $1$. Number of repetitions with different seeds: 10.\\

@@

\textbf{Figure 2 Supplementary Fig. 3:} Number of time steps were $4000$ (XXX maybe mention here and other above stating "except otherwise stated" or so XXX). Number of identical mean-field networks: $1000$.  Simulation time steps = $10^5$.\\
